### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	14:58:18	(Tue18.Mar)

\ai{The reviewer has a point. But since there are 3 occurrences of the covariance processing time, including the total time GPU processing time would introduce three new lines. We feel this would clutter the plot unnecessarily as it is fairly easy derive the total time by looking at the current plots. Putting the total processing time in the MATLAB/C total time figure is an option, but then a logarithmic y-scale would necessary and detail would be lost.}

>>>>

\ai{The reviewer has a point. But since there are 3 occurrences of the covariance processing time, including the total GPU processing time would introduce three new lines. We feel this would clutter the plot unnecessarily as it is fairly easy to derive the total time by looking at the current plots. Putting the total processing time in the MATLAB/C total time figure is an option, but then a logarithmic y-scale would necessary and detail would be lost. In stead we have included a remark in the caption saying the total GPU time is the sum of all the lines.}
